### 2021-08-06 paper/paper.tex
updated PID discussion and removed those TODOs

The results of this comparison are visualized in Figure~\ref{fig:PID-Euler}.
Clearly, \trixi is more than 2x faster than the Fortran code FLUXO
while both implement the same numerical methods. This demonstrates the
suitability of Julia for this kind of simulation-focused scientific computing.

@@

@@

\todo{TODO: add Intel discussion} % TODO: Andrew

\todo{TODO: alter slightly with MHD results} % TODO: Andrew

\todo{TODO: \trixi runs need redone due to further improvements} % TODO: Andrew

>>>>

The results of these performance comparisons are visualized for the 3D compressible Euler
in Figure~\ref{fig:PID-Euler} and for the 3D ideal MHD equations in Figure~\ref{fig:PID-MHD}.
We present the PID timings for both codes in the top portion of these two Figures as well as
a relative comparison using FLUXO as reference. Therefore, smaller values in the bottom portion
the Figures~\ref{fig:PID-Euler} and \ref{fig:PID-MHD} are better.

@@

From these results, it is clear that \trixi is more than 2x faster for the compressible Euler equations
and more than 1.5x faster for the ideal MHD equations than the Fortran code FLUXO.
We ran the same PID tests in FLUXO compiled with GCC v6.4.0 but found that
the Intel was between $5\%$ to $23\%$ faster.
Thus, only results from the Intel compiler are included.
It is also possible to see the additional computational overhead for the entropy conservative, flux
differencing DG methods for both physical models. This is because the numerical fluxes are more complex, in
terms of computational effort, and require special care to optimize their performance~\cite{hendrik_blog}.
We reiterate that both codes implement the same numerical nodal DG methods on curvilinear meshes used in these tests.
This demonstrates the suitability of Julia for this kind of simulation-focused scientific computing.

@@
